Theoretical evaluation of the potential advantages of cloud IDEs for research and didactics

### 2019-07-13 che.tex
removed even more, so i only have 12 pages

\section{Introduction}
\label{sec:Introduction}
Children look into the clouds and count sheep. 
Developers look into the clouds and check their applications.  
Cloud technologies are already state of the art, enabling global players to run applications on a world-scale.
The market-leaders stocked up their portfolios with  a  variety  of  different  cloud  technologies,  ranging from cloud computing, cloud storage, database-as-a-service or rented authentication. 
Modern software needs to be scalable, self-contained, and should run on any device, as well as in the cloud.  
This trend is also visible in Google searches \ref{fig:digdocker}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\linewidth]{imgs/DigDocker}
	\caption{Rising interest in Cloud Tec, Data provided by Google Trends}
	\label{fig:digdocker}	
\end{figure}

Figure \ref{fig:digdocker} shows the steadily rising interest in the most popular cloud technologies. 
Docker is a container-engine enabling OS-Virtualization, Kubernetes is a Container-Platform manager and OpenShift is a software-suite based on Kubernetes. 
These technologies will be summarized in \ref{subsec:Req}.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{imgs/Che_Workflow}
	\caption[Che Workflow]{Che Workflow}
	\label{fig:cheworkflow}
\end{figure}
\newpage

@@

The artifacts (whether containers or pods) produced with Che are self-contained and immutable, therefore every result is reproducible. 
Any further development is incremental on the existing images and keeps old artifacts stable. 
As the code is fully build inside containers and are already run remotely, the famous “It works on my Machine!” is eliminated. 
This does not only enhance deployments, but also has a big impact on quality assurance and the motivation of developers. 
You can keep multiple projects in a single workspace and launch multiple pods at once, running the full environment. 
The behavior of this multi-pod is unified and testable, making a stable release of full environments possible. 
This is one of the primary goals of the DevOps approach \cite{JA16}. 
\newpage
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, therefore 50\% of the research results were not reproducible.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage. 
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multi-pod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided.

@@

\subsection{Vulnerability}
The last problem is the vulnerability to malevolent users. 
Someone who already is in possession of a valid account can drain the shared resources of a full cluster, therefore blocking  any  other  user  from  work.
This  can  also  be achieved by human error. 
It is therefore important to not only restrict access to project resources, but also the double-check and guard the releases.
\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity only universities will be addressed.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With suitable material provided, it's easy to learn cloud native development, DevOps or Cloud-Operations. 
Even complicated topics, such as micro-services and IoT-applications can easily be adapted inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components as well as team-work to succeed with Che.

>>>>

\section{Introduction}
\label{sec:Introduction}
Children look into the clouds and count sheep. 
Developers look into the clouds and check their applications.  
Cloud technologies are already state of the art, enabling global players to run applications on a world-scale.
The market-leaders stocked up their portfolios with  a  variety  of  different  cloud  technologies,  ranging from cloud computing, cloud storage, database-as-a-service or rented authentication. 
Modern software needs to be scalable, self-contained, and should run on any device, as well as in the cloud.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{imgs/Che_Workflow}
	\caption[Che Workflow]{Che Workflow}
	\label{fig:cheworkflow}
\end{figure}

@@

The artifacts (whether containers or pods) produced with Che are self-contained and immutable, therefore every result is reproducible. 
Any further development is incremental on the existing images and keeps old artifacts stable. 
As the code is fully build inside containers and are already run remotely, the famous “It works on my Machine!” is eliminated. 
This does not only enhance deployments, but also has a big impact on quality assurance and the motivation of developers. 
You can keep multiple projects in a single workspace and launch multiple pods at once, running the full environment. 
The behavior of this multi-pod is unified and testable, making a stable release of full environments possible. 
This is one of the primary goals of the DevOps approach \cite{JA16}.

\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, therefore 50\% of the research results were not reproducible.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage.

@@

\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity only universities will be addressed.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With suitable material provided, it's easy to learn cloud native development, DevOps or Cloud-Operations. 
Even complicated topics, such as micro-services and IoT-applications can easily be adapted inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components as well as team-work to succeed with Che.
